How to Avoid OOTA Without Really Trying

### 2024-09-03 paper/ootavacuous.tex
asplos: Cite Jay Richards's and Mark Batty's tool
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

Other workers recommend various procedures to identify and avoid OOTA
cycles~\cite{Lahav:2017:RSC:3062341.3062352,Sinclair:2017:CAR:3079856.3080206,Lee:10.1145/3385412.3386010,MarkBatty2019ModularRelaxedDependenciesOOTA},
but none of these have been looked upon favorably by C++ implementers.
Many of these workers appear to have abandoned this effort, but as of
2024, Mark Batty is persisting with modular relaxed dependencies, which
may have the added ability of checking compiler optimizations.
@@@ cite web site.

@@

One advantage that tools often have over C++ implementations is the
ability to devote much more computational power to the problem at hand.
In fact, some tools respond to excessive complexity by consuming all
available CPU and memory, which can also be interpreted as a good and
sufficient warning message.

>>>>

Other workers recommend various procedures to identify and avoid OOTA
cycles~\cite{Lahav:2017:RSC:3062341.3062352,Sinclair:2017:CAR:3079856.3080206,Lee:10.1145/3385412.3386010,MarkBatty2019ModularRelaxedDependenciesOOTA},
but none of these have been looked upon favorably by C++ implementers.
Many of these workers appear to have abandoned this effort, but as of
2024, Mark Batty is persisting with modular relaxed dependencies, which
may have the added ability of checking compiler
optimizations~\cite{JayRichards2024SymbolicMrder}.

@@

One advantage that tools often have over C++ implementations is the
ability to devote much more computational power to the problem at
hand~\cite{JayRichards2024SymbolicMrder}.
In fact, some tools respond to excessive complexity by consuming all
available CPU and memory, which can also be interpreted as a good and
sufficient warning message.
